Di seguito sono riportati i riferimenti bibliografici degli articoli usati per la
revisione sistematica della letteratura.
\newline~\newline
[S1] Qingzhou L., Farah H., Lamyaa E., Darko M. (2014) “An Empirical
Analysis of Flaky Tests”. Proceedings of the 22nd ACM SIGSOFT International
Symposium on Foundations of Software Engineering, Hong Kong, China, 2014.
\newline~\newline
S2] Jonathan B., Gail K., Eric M., Mohan D. (2015) “Efficient
Dependency Detection for Safe Java Test Acceleration”. Proceedings of the 2015
10th Joint Meeting on Foundations of Software Engineering, Bergamo, Italy, 2015.
\newline~\newline
[S3] Zebao G., Yalan L., Myra B. C., Atif M. M., Zhen W. (2015) “Making
system user interactive tests repeatable: when and what should we control?”. ICSE
‘15: Proceedings of the 37th International Conference on Software Engineering –
Volume 1.
\newline~\newline
[S4] Alex G., August S., Farah H., Darko M. (2015) “Reliable Testing:
Detecting State-polluting Tests to Prevent Test Dependency”. Proceedings of the
2015 International Symposium on Software Testing and Analysis, Baltimore MD, USA, 2015.
\newline~\newline
[S5] Milos G., Lamyaa E., Darko M. (2015) “Practical regression test
selection with dynamic file dependencies”. ISSTA 2015: Proceedings of the 2015
International Symposium on Software Testing and Analysis.
\newline~\newline
[S6] Lam W, Zhang S, Ernst MD (2015) “When tests collide: Evaluating
and coping with the impact of test dependence”.
\newline~\newline
[S7] Shi A., Gyori, A., Legunsen O., Marinov D. (2016) ”Detecting
Assumptions on Deterministic Implementations of Non-deterministic Specifications”. Proceedings of the 2016 International Conference on Software Testing, Verification and Validation, USA.
\newline~\newline
[S8] Thomas R., Waldemar H., Philipp L., Stefan S (2017). “An Empirical Analysis of Build Failures in the Continuous Integration Workflows of Java-based
Open-source Software”. Proceedings of the 14th International Conference on Mining Software Repositories, Buenos Aires, Argentina, 2017.
\newline~\newline
[S9] Candido, J., Melo L., D’Amorim, M. (2017) “Test suite parallelization in open-source projects: A study on its usage and impact”. ASE 2017 – Proceedings
of the 32nd IEEE/ACM International Conference on Automated Software
Engineering.
\newline~\newline
[S10] Fabio P., Andy Z. (2015) “Does Refactoring of Test Smells Induce Fixing Flaky Tests?”. International Conference on Software Maintenance and
Evolution, Shanghai, China, 2017.
\newline~\newline
[S11] Labuschagne, A., Inozemtseva, L., Holmes, R. (2017) “Measuring
the cost of regression testing in practice: a study of Java projects using continuous integration”. Proceedings of the ACM SIGSOFT Symposium on the Foundations of Software Engineering August 2017.
\newline~\newline
[S12] Jonathan B., Owolabi L., Michael H., Lamyaa E., Tifany Y., Darko M. (2018) “DeFlaker: Automatically Detecting Flaky Tests”. Proceedings of the 40th International Conference on Software Engineering, Gothenburg, Sweden, 2018.
\newline~\newline
[S13] Swapna T., Chandani S., Na M. (2018) “An Empirical Study of Flaky Tests in Android”. International Conference on Software Maintenance and Evolution, Madrid, Spain, 2018.
\newline~\newline
[S14] Md T. R., Peter C. R. (2018) “The Impact of Failing, Flaky, and High Failure Tests on the Number of Crash Reports Associated with Firefox Builds”. Proceedings of the 2018 26th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering, Lake Buena Vista FL, USA, 2018.
\newline~\newline
[S15] Gambi, A., Bell, J., Zeller, A. (2018) “Practical Test Dependency Detection Proceedings”. 2018 IEEE 11th International Conference on Software Testing, Verification and Validation, ICST 2018.
\newline~\newline
[S16] Eck M., Palomba F., Castelluccio M., Bacchelli A. (2019)
“Understanding Flaky Tests: The Developer’s Perspective”. Proceedings of the 2019 27th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering, Tallinn, Estonia, 2019.
\newline~\newline
[S17] Wing L., Patrice G., Suman N., Anirudh S., Suresh T. (2019) “Root Causing Flaky Tests in Large-scale Industrial Setting”. Proceedings of the 28th ACM SIGSOFT International Symposium on Software Testing and Analysis, Beijing, China, 2019.
\newline~\newline
[S18] Armin N., Peter C. R.,Weiyi S. (2019) “Bisecting commits and
modeling commit risk during testing”. ESEC/FSE 2019: Proceedings of the 2019 27th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering.
\newline~\newline
[S19] Kai Presler-M., Eric H., Sarah H., Kathryn S. (2019) “Wait, Wait. No, Tell Me. Analysing Selenium Configuration Effects on Test Flakiness”. 14th International Workshop on Automation of Software Test, Montreal, QC, Canada, 2019.
\newline~\newline
[S20] August S., Wing L., Reed O., Tao X., Darko M. (2019) ” iFixFlakies: A Framework for Automatically Fixing Order-dependent Flaky Tests” In Proceedings of the 2019 27th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering, Tallinn, Estonia, 2019.
\newline~\newline
[S21] Biagiola M., Stocco A., Mesbah A., Ricca F., Tonella P. (2019) “Web test dependency detection”. ESEC/FSE 2019: Proceedings of the 2019 27th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering.
\newline~\newline
[S22] August S., Jonathan B., Darko M. (2017) “Mitigating the Effects of Flaky Tests on Mutation Testing”. Proceedings of the 28th ACM SIGSOFT International Symposium on Software Testing and Analysis, Beijing, China, 2017.
\newline~\newline
[S23] Andreas S., Marvin K., Gordon F. (2019) “Testing Scratch Programs Automatically”. Proceedings of the 2019 27th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering, Tallinn, Estonia, 2019.
\newline~\newline
[S24] Pontes F., Gheyi R., Souto S., Garcia A., Ribeiro M. (2019) “Java reflection API: revealing the dark side of the mirror”. ESEC/FSE 2019: Proceedings of the 2019 27th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering.
\newline~\newline
[S25] Böhme M. (2019) “Assurance in software testing: a roadmap”. ICSE- NIER ‘19: Proceedings of the 41st International Conference on Software Engineering: New Ideas and Emerging Results.
\newline~\newline
[S26] Schwahn O., Coppik N., Winter S., Suri N. (2019) “Assessing the
state and improving the art of parallel testing for C”. ISSTA 2019: Proceedings of the 28th ACM SIGSOFT International Symposium on Software Testing and Analysis.
\newline~\newline
[S27] Zhiyu F., (2019) “A Systematic Evaluation of Problematic Tests
Generated by EvoSuite”. 41st International Conference on Software Engineering: Companion Proceedings, Montreal, QC, Canada, 2019.
\newline~\newline
[S28] Wing L., Reed O., August S., Darko M., Tao X. (2019) “iDFlakies: A Framework for Detecting and Partially Classifying Flaky Tests”. 12th IEEE Conference on Software Testing, Validation and Verification, Xi’an, China, 2019.
\newline~\newline
[S29] Morán, J., Augusto, C., Bertolino, A., De La Riva, C., Tuya, J.
(2019) “Debugging flaky tests on web applications” WEBIST 2019 – Proceedings of the 15th International Conference on Web Information Systems and Technologies.
\newline~\newline
[S30] Palomba F., Zaidman A. (2019)” The Smell of Fear: On the Relation Between Test Smells and Flaky Tests”. Empirical Software Engineering, Salerno, Italy, 2019.