\fancyhead[L]{APPENDICE A}
\fancyhead[C]{}
Di seguito sono riportati i riferimenti bibliografici degli articoli usati per la
revisione sistematica della letteratura.
\newline~\newline
[S1] \textbf{Qingzhou L., Farah H., Lamyaa E., Darko M.} (2014) “An Empirical Analysis of Flaky Tests”. \emph{Proceedings of the 22nd ACM SIGSOFT International Symposium on Foundations of Software Engineering, Hong Kong, China, 2014.}
\newline~\newline
[S2] \textbf{Jonathan B., Gail K., Eric M., Mohan D.} (2015) “Efficient Dependency Detection for Safe Java Test Acceleration”. \emph{Proceedings of the 2015 10th Joint Meeting on Foundations of Software Engineering, Bergamo, Italy, 2015.}
\newline~\newline
[S3] \textbf{Zebao G., Yalan L., Myra B. C., Atif M. M., Zhen W.} (2015) “Making system user interactive tests repeatable: when and what should we control?”. \emph{ICSE‘15: Proceedings of the 37th International Conference on Software Engineering-Volume 1.}
\newline~\newline
[S4] \textbf{Alex G., August S., Farah H., Darko M.}(2015) “Reliable Testing: Detecting State-polluting Tests to Prevent Test Dependency”. \emph{Proceedings of the 2015 International Symposium on Software Testing and Analysis, Baltimore MD, USA, 2015.}
\newline~\newline
[S5] \textbf{Milos G., Lamyaa E., Darko M.} (2015) 
“Practical regression test selection with dynamic file dependencies”. \emph{ISSTA 2015: Proceedings of the 2015
International Symposium on Software Testing and Analysis.}
\newline~\newline
[S6] \textbf{Lam W, Zhang S, Ernst MD}(2015) “When tests collide: Evaluating and coping with the impact of test dependence”.
\newline~\newline
[S7] \textbf{Shi A., Gyori, A., Legunsen O., Marinov D.} (2016) ”Detecting Assumptions on Deterministic Implementations of Non-deterministic Specifications”.\emph{ Proceedings of the 2016 International Conference on Software Testing, Verification and Validation, USA.}
\newline~\newline
[S8] \textbf{Thomas R., Waldemar H., Philipp L., Stefan S.} (2017). “An Empirical Analysis of Build Failures in the Continuous Integration Workflows of Java-based Open-source Software”. \emph{Proceedings of the 14th International Conference on Mining Software Repositories, Buenos Aires, Argentina, 2017.}
\newline~\newline
[S9] \textbf{Candido, J., Melo L., D’Amorim, M.} (2017) “Test suite parallelization in open-source projects: A study on its usage and impact”. \emph{ASE 2017 – Proceedings of the 32nd IEEE/ACM International Conference on Automated Software
Engineering.}
\newline~\newline
[S10] \textbf{Fabio P., Andy Z.} (2015) “Does Refactoring of Test Smells Induce Fixing Flaky Tests?”. \emph{International Conference on Software Maintenance and Evolution, Shanghai, China, 2017.}
\newline~\newline
[S11] \textbf{Labuschagne, A., Inozemtseva, L., Holmes, R.} (2017) “Measuring the cost of regression testing in practice: a study of Java projects using continuous integration”. \emph{Proceedings of the ACM SIGSOFT Symposium on the Foundations of Software Engineering August 2017.}
\newline~\newline
[S12] \textbf{Jonathan B., Owolabi L., Michael H., Lamyaa E., Tifany Y., Darko M.} (2018) “DeFlaker: Automatically Detecting Flaky Tests”. \emph{Proceedings of the 40th International Conference on Software Engineering, Gothenburg, Sweden, 2018.}
\newline~\newline
[S13] \textbf{Swapna T., Chandani S., Na M.} (2018) “An Empirical Study of Flaky Tests in Android”. \emph{International Conference on Software Maintenance and Evolution, Madrid, Spain, 2018.}
\newline~\newline
[S14] \textbf{Md T. R., Peter C. R.} (2018) “The Impact of Failing, Flaky, and High Failure Tests on the Number of Crash Reports Associated with Firefox Builds”. \emph{Proceedings of the 2018 26th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering, Lake Buena Vista FL, USA, 2018.}
\newline~\newline
[S15] \textbf{Gambi, A., Bell, J., Zeller, A.} (2018) “Practical Test Dependency Detection Proceedings”. \emph{2018 IEEE 11th International Conference on Software Testing, Verification and Validation, ICST 2018.}
\newline~\newline
[S16] \textbf{Eck M., Palomba F., Castelluccio M., Bacchelli A.} (2019)
“Understanding Flaky Tests: The Developer’s Perspective”. \emph{Proceedings of the 2019 27th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering, Tallinn, Estonia, 2019.}
\newline~\newline
[S17] \textbf{Wing L., Patrice G., Suman N., Anirudh S., Suresh T.} (2019) “Root Causing Flaky Tests in Large-scale Industrial Setting”. \emph{Proceedings of the 28th ACM SIGSOFT International Symposium on Software Testing and Analysis, Beijing, China, 2019.}
\newline~\newline
[S18] \textbf{Armin N., Peter C. R.,Weiyi S.} (2019) “Bisecting commits and modeling commit risk during testing”. \emph{ESEC/FSE 2019: Proceedings of the 2019 27th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering.}
\newline~\newline
[S19] \textbf{Kai Presler-M., Eric H., Sarah H., Kathryn S.} (2019) “Wait, Wait. No, Tell Me. Analysing Selenium Configuration Effects on Test Flakiness”. \emph{14th International Workshop on Automation of Software Test, Montreal, QC, Canada, 2019.}
\newline~\newline
[S20] \textbf{August S., Wing L., Reed O., Tao X., Darko M.} (2019) ”iFixFlakies: A Framework for Automatically Fixing Order-dependent Flaky Tests” \emph{In Proceedings of the 2019 27th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering, Tallinn, Estonia, 2019.}
\newline~\newline
[S21] \textbf{Biagiola M., Stocco A., Mesbah A., Ricca F., Tonella P.} (2019) “Web test dependency detection”. \emph{ESEC/FSE 2019: Proceedings of the 2019 27th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering.}
\newline~\newline
[S22] \textbf{August S., Jonathan B., Darko M.} (2017) “Mitigating the Effects of Flaky Tests on Mutation Testing”. \emph{Proceedings of the 28th ACM SIGSOFT International Symposium on Software Testing and Analysis, Beijing, China, 2017.}
\newline~\newline
[S23] \textbf{Andreas S., Marvin K., Gordon F.} (2019) “Testing Scratch Programs Automatically”. \emph{Proceedings of the 2019 27th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering, Tallinn, Estonia, 2019.}
\newline~\newline
[S24] \textbf{Pontes F., Gheyi R., Souto S., Garcia A., Ribeiro M.} (2019) “Java reflection API: revealing the dark side of the mirror”. \emph{ESEC/FSE 2019: Proceedings of the 2019 27th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering.}
\newline~\newline
[S25] \textbf{Böhme M.} (2019) “Assurance in software testing: a roadmap”. \emph{ICSE- NIER ‘19: Proceedings of the 41st International Conference on Software Engineering: New Ideas and Emerging Results.}
\newline~\newline
[S26] \textbf{Schwahn O., Coppik N., Winter S., Suri N.} (2019) “Assessing the state and improving the art of parallel testing for C”. \emph{ISSTA 2019: Proceedings of the 28th ACM SIGSOFT International Symposium on Software Testing and Analysis.}
\newline~\newline
[S27] \textbf{Zhiyu F.} (2019) “A Systematic Evaluation of Problematic Tests Generated by EvoSuite”. \emph{41st International Conference on Software Engineering: Companion Proceedings, Montreal, QC, Canada, 2019.}
\newline~\newline
[S28] \textbf{Wing L., Reed O., August S., Darko M., Tao X.} (2019) “iDFlakies: A Framework for Detecting and Partially Classifying Flaky Tests”. \emph{12th IEEE Conference on Software Testing, Validation and Verification, Xi’an, China, 2019.}
\newline~\newline
[S29] \textbf{Morán, J., Augusto, C., Bertolino, A., De La Riva, C., Tuya, J.}
(2019) “Debugging flaky tests on web applications” \emph{WEBIST 2019-Proceedings of the 15th International Conference on Web Information Systems and Technologies.}
\newline~\newline
[S30] \textbf{Palomba F., Zaidman A.} (2019)” The Smell of Fear: On the Relation Between Test Smells and Flaky Tests”. \emph{Empirical Software Engineering, Salerno, Italy, 2019.}